\chapter{Culture and Religion}
Part of my last years of living in Denmark aside from trying to settle there was getting the experience of the  old world. Having grown up in the new world, it is very easy to see in a performative aspect but also in many other ways as well. I am noting this as the cultural intensity found in the west is quite different from Europe to North America. In Europe, cultural identity is very strong while religion is not such a big deal. It seems as though there is a much bigger emphasis placed on things like food, family, and other cultural events that we might equate to the likeness of what thanksgiving or the 4th of July/Canada day means to us. I believe that within North America the presence of a strong cultural identity is far less. We have one, as would be expected of any place in the world, yet it is based more in the vein of individual importance of cultural heritage from whichever motherland we hail from. This is coupled alongside a much bigger influence of Religion in our lives. If you do not believe this, look at the prevalence of the Bible Belt in the south and try to find something similar to that outside of the Vatican in Europe. I can almost guarantee you will not find anything like this for individuals that belong to the millenial generation. I think that India is very much like Europe in this regard as cultural identity is quite strong and the layers go on for quite some depth. Having been raised in an "American" house, much of the cultural stuff has been lost within our world. This is not to say that we are substantially further away from India, but things like Darshan, puja and appropriate ways to act around elders are quiet different in both places. Many of the cultural bits and pieces that are different from Indian society back home will be quite strange, but it is not something that is out of reach. Rather this is always something that is within reach of your capabilities and abilities - I managed and I spent the greater portion of my adolescence rejecting Indian culture. Of course being in India will be far more intense than you may have expected but then again if you just allow yourself to realise that you have grown up with India Lite, it will become easier. How are you supposed to compare with these individuals  who have known this their entire life!? It might be synonymous to someone from India coming to the West and being expected to be as good as navigating the western landscape as you are. We all have different qualities. Your whole life you have been straddling the East and West in a balancing act that can only be described as damn impressive. It is not an easy feat, and it is something that takes time, energy, and practice. Upon arriving in India you will quickly understand that you do not have to do anything, the culture of this place is far more regional and family specific. You just need to do the same things that you grandparents or parents had you do and all of a sudden you will be enough. Religion here while still massively important, will be slightly less of a reason for doing or not doing certain life activities. You can just live life here to whatever degree you feel is enough and it will be okay! You do not need to maintain the culture if you dont want to. After all culture is dynamic and there are another 1.3 billion individuals who are also working to maintain the culture the same way that it has been maintained for the last 1000 years. Suddenly you can stop being a person of colour in the west and just a person.