\chapter{Trust of your countrymen}
Have you ever noticed that we place quite a lot of trust in other people of colour and more specifically with other Indian people?  For the first time I found myself surrounded by people that eat, drink, and act like me to varying degrees. Within the west we often applaud this and get excited when you start to build up a community of people of colour. This is different when you are in a world where everyone is a person of colour and we are all Indians. People suddenly just become people, and then your faith in humanity may or may not be crushed as a result of that. 1.3 billion people need to work in every niche of society which means that suddenly indian people are more than just taxi drivers and IT professionals. Indian people are in the military, police force, government, farms, construction, crime, etc etc. In this moment it is true that everyone simply looks out for his or herself and does not bother with anyone elses priorities because they do not matter. You are also Indian? Big fucking deal - there are another 1.3 billion people that are just like you. It will be difficult to trust your fellow countrymen while here because everyone is struggling to make a quick buck. This results in many people trying to pull a fast one to rob you without you knowing until it is too late. The issue with this robbery is that when you dont speak the regional language well enough, they will take you for a ride. They will know that you had money to get there in the first place and the name of the game is how can they work to get your money the fastest. This is not so easy but it is something they will be good with. If you are not careful you will lose money quite quickly across the board and put yourself in danger. This can always change over time as you lose your accent and develop a better one but it will take time. The issue that stands here is that you are not the first person that they will have tried this with, rather one of 1000s and you will likely be seeing this con for the first time. These stories go on for ages but ultimatley the mentality that persists amongst the majority of the country is what has kept our nation in such abject conditions. Only focusing on what will come today and how to make it through this day is a common narrative. That coupled with the belief that you are doing your duty by taking things day by day provides you with the current state of affairs which is also an issue on a larger scale. 